Singapore's Public Housing Affordability

### 2023-11-14 datastory.qmd
Project Update

### Assessing Affordability of Resale Flats in Singapore

```{r, eval=FALSE,echo=FALSE}

@@

### Conclusion

>>>>

### Assessing Affordability of Resale Flats in Singapore
<p style="text-align: justify;">
So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable for Singaporeans - compared with the average income earned. 
```{r, eval=FALSE,echo=FALSE}

@@

### Conclusion
<p style="text-align: justify;">
You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right! But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
</p>
